Search for Spatially Extended Fermi-LAT Sources Using Two Years of Flight Data

### 2011-07-29 extended_catalog/paper/extended_catalog.tex
draft improvements

In addition to these GeV $\gamma$-ray detections, a variety of
spatially extended sources have been detected in the Galactic plane at
\tev energies using Air Cherenkov detectors. Most prominent was a
survey of the Galactic plane using the High Energy Stereoscopic System
(H.E.S.S) which presented 14 spatially extended sources
(\cite{hess_plane_survey}) sources with extensions varying from
$~0.1\deg$ to $~0.25\deg$. In fact, within our Galaxy only very few
sources (most notably the $\gamma$-ray binaries
LS\,5039\cite{HESSLS5039}, LS I+61-303\cite{MAGICLSI, VERITASLSI} and
HESS\,J0632+057\cite{HESS0632} are amongst the few Galactic sources
for which no significant extension was detected at \tev
energies. Given these findings, it can be expected that if the source
population at GeV energies has similar properties, that at least some
of the Fermi-LAT sources in our Galaxy should be spatially extended at
GeV energies.

@@

We also performed a search for extended sources using photons only between
10 \gev and 100 \gev. Even though we are testing the same sources, this
approach is complimentary because the Galactic diffuse emission is even
less dominant above 10 \gev. Furthermore, source confusion becomes less of
a problem since most LAT sources are not significant at energies above 10
\gev.  Using higher energies, we might expect to detect harder sources in
more complicated regions. This is especially beneficial
for regions near pulsars which cutoff before 10 \gev
and was successfully used in detecting HESS J1825-137
and MSH 15-52 with the LAT (\cite{msh1552,fermi_hess_j1825}).

@@

% 2FGL J1856.2+0450c = P72Y3047 for
As an example of why this is important, we describe the test of 2FGL
J1856.2+0450c for extension.  Figure~\ref{example_bad_fit} shows
a smoothed counts map using photons with energy above 1 \gev. In
the map, the Galactic and isotropic diffuse emission are subtracted.
A 2FGL source 2FGL J1856.2+0450c was found at the position
$(l,b)=(37.25\deg,0.84\deg)$.  We find that there appears to be overall
some large-scale residual in the diffuse emission along the Galactic
plane. As a result, 2FGL J1856.2+0450c fits to a
large extension of 1.83\deg and the result is statistically significant
with \tsext=103.6 (using \pointlike).  By looking at the residuals, it is clear that this
complicated region is not well fit even though the source's extension is
statistically significant. For this reason, we have to perform a series
of further analysis for all of the sources that are found with \tsext=16.
% information came from
% /nfs/slac/g/ki/ki03/lande/extended_catalog/2FGL/v15/standard_analysis/spectral_emin_1000_v1/P72Y3047/v1/results_followup_P72Y3047.yaml

@@

% 3 PWN
Three pulsar wind nebula Vela X, MSH 15-52, and HESS J1825-137 were
included in 2FGL (\cite{velax,msh1552,fermi_hess_j1825}).  Using photons
with energy above 10 \gev, we significantly detected the extension of
HESS J1825-137.  To improve the model of this source, we removed the
nearby catalog source 2FGL J1823.1-1338c which is part of the extended
source.  To avoid the nearby pulsar PSR J1509-5850, MSH 15-52 must be
analyzed at high energies.  Using photons with energies above 10 \gev,
we fit the extension of MSH 15-52 to be consistent with the published
size with an extension significance of \tsext=7.2.  Our analysis was
unable to resolve Vela X which would have required removing the pulsed
photons from the Vela pulsar. This is beyond the scope of this paper.

@@

The results are summarized in table~\ref{known_extended_sources}.
This table includes the best fit position and extension of these
sources when fitting them with a radially symmetric uniform disk spatial
model.  It also includes the best fit spectral model of each source.
The difficulty that out analysis had fitting the extension of several
of the already published extended sources should be used to emphasize
the overall difficultly in studying spatially extended sources in crowded
regions of the sky.

@@

To validate our method and assess systematic issues with our analysis,
we used \pointlike to test known AGN for extension.
\gev emission from AGN is believed to comes from the core of supermassive
blackholes in small regions in the core of distant galaxies.  AGN are
not expected to be spatially resolvable and therefore provide a good
calibration source to demonstrate the efficacy of our tool. Nevertheless,
it would be interesting if AGN could be spatially resolved and
there are theories that predict this (\cite{pair_halo_paper}).

Following 1FGL, the LAT collaboration published
a list of sources that had a high probability association with
AGN (\cite{first_agn_cat}).
1FGL had 709 AGN associated with 671 distinct
1FGL sources at high latitude ($|b|>10\deg$).  To avoid systematic
problems with AGN classification, we used only the 599 AGN which made
it into the clean AGN sample.  An AGN association is only considered
clean if it has a high probability of association $P\ge 80\%$, if it is
the only AGN associated with the 1FGL source, and if there are no flags
on the catalog source (\cite{first_cat}). These last two conditions are
especially important for our analysis.  Source confusion may look like
a spatially extended source and flagged catalog sources may correlate
with unmodeled structure in the diffuse emission.

Of the 599 ``clean'' AGN, we select 556 of these 1FGL sources which
we uniquely associate with a 2FGL source. We furthermore
restrict our select to the 515 of these AGN for which we fit $\ts>25$
using \pointlike and photons with energy above 1 \gev.  Our intention
here is not to find the largest sample of AGN but simply
to find a good sample to test the systematics of our extended source
search.

Using the same extension fitting procedure as described above, we tested
these 515 AGN for extension. A histogram of the \tsext values computed
with \pointlike is shown in figure~\ref{agn_ts_ext}. Overlaid on the plot
is a $\chi^2/2$ distribution suggested by Wilks' Theorem.  This plot
shows a worse agreement with the theoretical distribution and
a discrepancy with 
our Monte Carlo study in figure~\ref{ts_ext_mc}.  But overall, the
distribution is good. No AGN get fit with a particularly significant
value of $\tsext$ and almost all of the AGN get fit with $\tsext<1$.
There where only two AGN with $\tsext>10$. The maximum had $\tsext=13.7$
whereas the maximum value expected theoretically by the $\chi^2/2$ distribution is
8.3. This result shows that there is some systematic with our
analysis but that it will not significantly affect our analysis.
% 8.3 number gotten from mathematica:
% PDF[ChiSquareDistribution[1], x]
% N[Solve[(1/2)*
%     Integrate[1/(E^(x/2)*(Sqrt[2*Pi]*Sqrt[x])), {x, TS, Infinity}] &=&  
%        1/515, TS]]

Several possible systematics could cause this discrepancy. The first is
that in our analysis we fit each source with a power-law spectral model.
AGN tend to have curved spectral and fitting with the wrong spectral
model might effect the value of \tsext. Nevertheless, since we use only
photons with energy above 1 \gev, this effect is not expected to be large.
Another possible source for the discrepancy is that \pointlike performs
a likelihood analysis without modeling the energy dispersion of the LAT.
This probably is not the cause because energy dispersion is expected to
be more significant at low energy and it would have also showed up with
the Monte Carlo simulations.

Another possible systematic may be due to source confusion to problems
with the background model. If the two sources were close, they may
be unresolvable and get fit as a more significant extended source.
It is also possible that there are lingering residuals in the diffuse
emission. Unmodeled parts of the diffuse emission could be filled in by
modeling point sources as being slightly extended.

@@

We should finally clarify that since the PSF was found empirically
from the shape of bright AGN, finding that the AGN we test are not
significantly extended is not surprising.  All this analysis shows
is that the we can significantly find sources larger than bright AGN
found by the LAT.  Trying to look for the extension of these AGN as a
population would require a more specialized analysis.

@@

\subsection{2FGL J0823.0-4246}
\label{section_2FGL_J0823.0-4246}

@@

The two year catalog source 2FGL J0823.0-4246 was found to be
extended using photons with energy between 1 \gev and 100 \gev.
We found an extension of $0.37\deg\pm0.03\deg$ and an extension
significance of $\tsext=46.1$.  The source was fit to a position of
$(l,b)=(260.32\deg,-3.28\deg)$.  Figure~\ref{1FGL_J0823.3-4248} shows a
counts map of this source.  This source is coincident with the one year
catalog source 1FGL J0823.3-4248.

To get a good fit of the source, we had to remove the nearby catalog
sources 2FGL J0823.4-4305 and 2FGL J0821.0-4254 which are part of the
extended source.  We tested the source for source confusion by fitting
it as two point sources. Because $\tsinc=21.9$ is smaller then \tsext,
we conclude that this is an extended source.  
These modifications are shown in
figure~\ref{1FGL_J0823.3-4248}.

@@

\todo[inline]{Add interpretations of Puppis A. Stefan volunteered to write this}

\subsection{2FGL J1627.0-2425c}
\label{section_2FGL_J1627.0-2425c}

@@

The two year catalog source 2FGL J1627.0-2425c was found to be
significantly extended when using photons with energies between 1 \gev
and 100 \gev.  The best fit extension was $0.53\deg\pm0.06\deg$ and the
best fit position is $(l,b)=(352.87\deg, 16.79\deg)$.
The extension significance was $\tsext=20.3$. 
This source is coincident with the one year catalog source 1FGL J1628.6-2419c.
A counts map showing this source is
seen in figure \ref{1FGL_J1628.6-2419c}.  To test for source confusion,
we also fit the source instead as two point sources. Since $\tsinc=19.3$
is smaller than \tsext, we conclude that this is an extended source.

@@

\subsection{2FGL J0851.7-4635}
\label{section_2FGL_J0851.7-4635}

@@

The two year catalog source 2FGL J0851.7-4635 was found to be
extended using photons with energies between 10 \gev and 100
\gev. We fit an extension of $1.12\deg\pm0.07\deg$ with an extension
significance of $\tsext=76.7$.  The source was fit to a position of
$(l,b)=(266.29\deg,-1.41\deg)$.  Figure~\ref{Vela_Jr} shows a counts
map of this source.

2FGL J0851.7-4635 is spatially coincident with the SNR Vela Jr.  Overlaid
on figure~\ref{Vela_Jr} are contours of Vela Jr. as seen in \tev by
H.E.S.S (\cite{vela_jr_hess}).  The \gev and \tev morphology match well.

\todo[inline]{Add interpretations of Vela Jr.. How to sync with upcoming
publication? Stefan volunteered to write this.}

To get a good fit of the source, we had to remove thee nearby catalog
sources 2FGL J0853.5-4711, 2FGL J0848.5-4535, and 2FGL J0855.4-4625
which are part of the extended source.  In addition, we relocalized
the position of the nearby catalog source 2FGL J0854.7-4501 to
$(l,b)=(266.24\deg,0.49\deg)$ to better fit its position at high energies
in the presence of of the eextended source.  In addition, we removed the
further away catalog sources 2FGL J0858.0-4815 and 2FGL J0901.7-4655
because they were not significant above 10 \gev.  After modifying
the region, we found that \tsinc=16.2 which is less than \tsext so we
conclude that the source is extended These modifications are shown in
figure~\ref{Vela_Jr}.

\subsection{2FGL J1615.0-5051}
\label{section_2FGL_J1615.0-5051}

@@

The two year catalog source 2FGL J1615.0-5051 was found to be
extended using photons with energies between 10 \gev and 100 \gev.
We found an extension of $0.33\deg\pm0.04\deg$ with an extension
significance of \tsext=16.6.  The source was fit to a position of
$(l,b)=(332.38\deg,-0.14\deg)$.  This source is coincident with the one
year catalog source 1FGL J1613.6-5100c.  Figure~\ref{1FGL_J1613.6-5100c}
shows a counts map of this source.

This source is less than 1\deg away from 2FGL J1615.2-5138 which is
also spatially extended (see section~\ref{section_2FGL_J1615.2-5138}).
To get a good fit of both sources, we had to model both sources as
being spatially extended and iteratively fit the position and extension
of each source until obtaining a global best fit.  Before doing this,
We removed from our model the source 2FGL J1614.9-5212 because it is
part of 2FGL J1615.2-5138's. Furthermore, we removed
the nearby catalog sources 2FGL J1619.7-5040c and 2FGL J1620.6-5111c
because they were not significant above 10 \gev.  These modifications
are further described in the caption to figure~\ref{1FGL_J1613.6-5100c}.
After modifying the region, we found that \tsinc=12.2 which is less than
\tsext so we conclude that the source is extended.

This source is spatially coincident with the extended \tev source HESS
J1616-508 (\cite{hess_plane_survey}).  In figure~\ref{1FGL_J1613.6-5100c},
contours of HESS J1616-508 are overlaid on 2FGL J1615.0-5051.
The H.E.S.S. experiment measured an extension $0.136\pm 0.008$
when fitting the source with an elliptical Gaussian spatial model.
This size corresponds to a 68\% source containment radius of
$\rsixeight\sim0.21\deg\pm0.01$. This size is comparable to the LAT size
$\rsixeight=0.27\deg\pm0.03$ (see section~\ref{compare_source_size}).
Figure~\ref{hess_seds} shows that the LAT spectrum of
2FGL J1615.0-5051 connects smoothly to the 
H.E.S.S spectrum of HESS J1616-508.

\todo[inline]{Add interpretations of HESS J1616-508.}

\subsection{2FGL J1615.2-5138}
\label{section_2FGL_J1615.2-5138}

The two year catalog source 2FGL J1615.2-5138 was found to be
extended using photons with energies between 10 \gev and 100 \gev.
We found an extension of $0.42\deg\pm0.03\deg$ with an extension
significance of \tsext=47.6.  The source was fit to a position
of $(l,b)=(331.66\deg,-0.66\deg)$.  This source is coincident
with the one year catalog source 1FGL J1614.7-5138c.  Because 2FGL
J1615.2-5138 is close to 2FGL J1615.0-5051, the same model described
in section~\ref{section_2FGL_J1615.0-5051} was used to analyze both
sources. Both sources can be seen in figure~\ref{1FGL_J1613.6-5100c}.
For 2FGL J1615.2-5138, \tsinc=37.6 which is less than \tsext so we
conclude that the source is extended.

This source is spatially coincident with the extended \tev source HESS
J1614-518 (\cite{hess_plane_survey}). In figure~\ref{1FGL_J1613.6-5100c},
contours of HESS J1614-518 are overlaid on 2FGL J1615.2-5138.
The H.E.S.S. experiment measured a Gaussian extension of
$\sigma=0.23\deg\pm0.02\deg$ and $\sigma=0.15\pm0.02$ in the semi-major
and semi-minor axis. This size corresponds to a 68\% containment size
of $\rsixeight=0.35\pm0.03\deg$ and $0.23\pm0.03$.  This elliptical size
matches well the LAT size of $\rsixeight\sim0.34\pm0.02$.
Figure~\ref{hess_seds} shows that the LAT spectrum of
2FGL J1615.2-5138 connects smoothly to the 
H.E.S.S spectrum of HESS J1614-518.

\todo[inline]{Add interpretations of HESS J1614-518. Stefan says to
use the Rowell et al, Suzaku observations.}

\subsection{2FGL J1632.4-4753c}
\label{section_2FGL_J1632.4-4753c}

@@

The two year catalog source 2FGL J1632.4-4753c was found to be
extended using photons with energies between 10 \gev and 100 \gev.
We fit an extension of $0.44\deg\pm0.04\deg$ with an extension
significance of \tsext=64.8.  The source was fit to a position of
$(l,b)=(336.41\deg,0.22\deg)$.  This source is coincident with the one
year catalog source 1FGL J1632.9-4802c.  Figure~\ref{1FGL_J1632.9-4802c}
shows a counts map of this source.

To get a good fit of the source, we had to remove from our model
three catalog sources 2FGL J1631.7-4720c, 2FGL J1630.2-4752, 2FGL
J1634.4-4743c.4-4820c that were part of the extended source..
We then iterativly relocalized the source 2FGL J1635.4-4717c
to $(l,b)=(337.230\deg,0.346\deg)$ and 2FGL J1636.3-4740c to
$(l,b)=(336.968\deg,-0.066\deg)$ while fitting the extension of
2FGL J1632.4-4753c.  In addition we removed from our model four
farther away two year catalog sources 2FGL J1638.0-4703c, 2FGL
J1628.1-4857c, 2FGL  J1630.1-4615, 2FGL J1639.8-4921c because they
were not significant above 10 \gev.  These modifications are shown in
figure~\ref{1FGL_J1632.9-4802c}.

To test for source confusion, we compared the likelihood fitting this
region as one extended source to the likelihood fitting this region as
two point sources. We found $\tsinc=40.9\loglikelihood\tsext$ which is less than \tsext
so we conclude that this is an extended source.

This extended source is spatially coincident with the extended \tev source HESS
J1632-478 (\cite{hess_plane_survey}).  In figure~\ref{1FGL_J1632.9-4802c},
contours of  HESS J1632-478 are overlaid on 2FGL J1635.4-4717c.
H.E.S.S measured an extension of $\sigma=0.21\pm0.05$ and
$0.06\pm0.04$ along the semi-major and semi-minor axes when fitting the source
with an elliptical Gaussian spatial model.  This corresponds to a 68\%
containment size of $\rsixeight=0.31\pm0.08$ and $0.09\pm0.06$ along the
semi-major and semi-minor axis. This size is consistent with the LAT size of
$\rsixeight=0.36\pm0.03$.
Figure~\ref{hess_seds} shows that the LAT spectrum of
2FGL J1635.4-4717c connects smoothly to the 
H.E.S.S spectrum of HESS J1632-478.

\todo[inline]{Add interpretation of HESS J1632-478.}

\subsection{2FGL J1837.3-0700c}
\label{section_2FGL_J1837.3-0700c}

@@

The two year catalog source 2FGL J1837.3-0700c was found to be
extended using photons with energies between 10 \gev and 100 \gev.
We fit an extension of $0.35\deg\pm0.08\deg$ with an extension
significance of $\tsext=20.2$.  The source was fit to a position of
$(l,b)=(25.08\deg,0.13\deg)$.  This source is coincident with the one
year catalog source 1FGL J1837.5-0659c.  Figure~\ref{1FGL_J1837.5-0659c}
shows a counts map of this source.

>>>>

In addition to these GeV $\gamma$-ray detections, a variety of
spatially extended sources have been detected in the Galactic plane at
\tev energies using Air Cherenkov detectors. Most prominent was a
survey of the Galactic plane using the High Energy Stereoscopic System
(H.E.S.S) which presented 14 spatially extended sources
(\cite{hess_plane_survey}) sources with extensions varying from
$~0.1\deg$ to $~0.25\deg$. In fact, within our Galaxy only very few
sources (most notably the $\gamma$-ray binaries
LS\,5039 (\cite{HESSLS5039}), LS I+61-303 (\cite{MAGICLSI, VERITASLSI}) and
HESS\,J0632+057 (\cite{HESS0632}) are amongst the few Galactic sources
for which no significant extension was detected at \tev
energies. Given these findings, it can be expected that if the source
population at GeV energies has similar properties, that at least some
of the Fermi-LAT sources in our Galaxy should be spatially extended at
GeV energies.

@@

We also performed a search for extended sources using photons only between
10 \gev and 100 \gev. Even though we are testing the same sources, this
approach is complimentary because the Galactic diffuse emission is even
less dominant above 10 \gev. Furthermore, source confusion becomes less of
a problem since most LAT sources are not significant at energies above 10
\gev.  Using higher energies, we might expect to detect harder sources in
more complicated regions. This is especially beneficial
for regions near pulsars which cutoff before 10 \gev
and was successfully used in detecting HESS\,J1825-137
and MSH 15-52 with the LAT (\cite{msh1552,fermi_hess_j1825}).

@@

% 2FGL J1856.2+0450c = P72Y3047 for
As an example of why this is important, we describe the test of 2FGL
J1856.2+0450c for extension.  Figure~\ref{example_bad_fit} shows
a smoothed counts map using photons with energy above 1 \gev. In
the map, the Galactic and isotropic diffuse emission are subtracted.
A 2FGL source 2FGL\,J1856.2+0450c was found at the position
$(l,b)=(37.25\deg,0.84\deg)$.  We find that there appears to be overall
some large-scale residual in the diffuse emission along the Galactic
plane. As a result, 2FGL\,J1856.2+0450c fits to a
large extension of 1.83\deg and the result is statistically significant
with \tsext=103.6 (using \pointlike).  By looking at the residuals, it is clear that this
complicated region is not well fit even though the source's extension is
statistically significant. For this reason, we have to perform a series
of further analysis for all of the sources that are found with \tsext=16.
% information came from
% /nfs/slac/g/ki/ki03/lande/extended_catalog/2FGL/v15/standard_analysis/spectral_emin_1000_v1/P72Y3047/v1/results_followup_P72Y3047.yaml

@@

% 3 PWN
Three pulsar wind nebula Vela X, MSH 15-52, and HESS\,J1825-137 were
included in 2FGL (\cite{velax,msh1552,fermi_hess_j1825}).  Using photons
with energy above 10 \gev, we significantly detected the extension of
HESS\,J1825-137.  To improve the model of this source, we removed the
nearby catalog source 2FGL\,J1823.1-1338c which is part of the extended
source.  To avoid the nearby pulsar PSR J1509-5850, MSH 15-52 must be
analyzed at high energies.  Using photons with energies above 10 \gev,
we fit the extension of MSH 15-52 to be consistent with the published
size with an extension significance of \tsext=7.2.  Our analysis was
unable to resolve Vela X which would have required removing the pulsed
photons from the Vela pulsar. This is beyond the scope of this paper.

@@

The results are summarized in table~\ref{known_extended_sources}.
This table includes the best fit position and extension of these
sources when fitting with a radially symmetric uniform disk spatial
model.  It also includes the best fit spectral model of each source.
The difficulty that out analysis had fitting the extension of several
of the already published extended sources should be used to emphasize
the overall difficultly in studying spatially extended sources in crowded
regions of the sky.

@@

To validate our method, we test associated AGN for extension.  \gev
emission from AGN is believed to comes from the core of supermassive
blackholes in small regions in the core of distant galaxies. Therefore AGN
are not expected to be spatially resolvable and provide a good calibration
source to demonstrate the efficacy of our tool. Nevertheless, it would
be interesting if AGN could be spatially resolved and there are theories
that predict this (\cite{pair_halo_paper}).

Following 1FGL, the LAT collaboration published a list of sources that
had a high probability association with AGN (\cite{first_agn_cat}).
1FGL had 709 1FGL sources associated with 671 distinct AGN at high
latitude ($|b|>10\deg$).  An upcoming publication by the LAT collaboration
using two years of data and the 2FGL catalog associates 1017 2FGL sources
with AGN.  To avoid systematic problems with AGN classification, we
selected the 815 AGN which made it into the clean AGN sample.  An AGN
association is considered clean only if it has a high probability
of association $P\ge 80\%$, if it is the only AGN associated with the
catalog source, and if there are no flags on the source in 2FGL. These
last two conditions are especially important for our analysis. Source
confusion may look like a spatially extended source and flagged catalog
sources may correlate with unmodeled structure in the diffuse emission.

Of the 815 clean AGN, we select 775 of these 2FGL sources which
are significant above 1 \gev and fit each of them for extnesion.
A histogram of the \tsext values computed for these AGN is shown
in figure~\ref{agn_ts_ext}. Overlaid on the plot is a $\chi^2/2$
distribution suggested by Wilks' Theorem.  The \tsext distribution
for AGN shows good agreement between the theoretical distribution.
Two sources had $\tsext>9$.  One was due to incorrectly
    pruning a nearby catalog sources and the other was due to failure
    of convergence of the point hypothesis.
This result demonstrates that we can use \tsext as a measure of the
statistical significance of the detection of the extension of a source.

@@

We should finally clarify that the LAT PSF used in this study was
determined empirically by fitting the observed shape of bright AGN
(\cite{lat_on_orbit_psf}).  Therefore, finding that the AGN we test are
not extended is not surprising.  All this analysis shows is that the we
can search for sources significantly brighter than AGN.  Trying to look
for the extension of AGN would require a more specialized analysis.

@@

\subsection{2FGL\,J0823.0-4246}
\label{section_2FGL_J0823.0-4246}

@@

The two year catalog source 2FGL\,J0823.0-4246 was found to be
extended using photons with energy between 1 \gev and 100 \gev.
We found an extension of $0.37\deg\pm0.03\deg$ and an extension
significance of $\tsext=46.3$.  The source was fit to a position of
$(l,b)=(260.32\deg,-3.28\deg)$.  Figure~\ref{1FGL_J0823.3-4248} shows a
counts map of this source.  This source is coincident with the one year
catalog source 1FGL\,J0823.3-4248.

To get a good fit of the source, we had to remove the nearby catalog
sources 2FGL\,J0823.4-4305 and 2FGL\,J0821.0-4254 which are part of the
extended source.  We tested the source for source confusion by fitting
it as two point sources. Because $\tsinc=22.1$ is smaller then \tsext,
we conclude that this is an extended source.  
These modifications are shown in
figure~\ref{1FGL_J0823.3-4248}.

@@

\todo[inline]{Add interpretations of Puppis A.}

\subsection{2FGL\,J1627.0-2425c}
\label{section_2FGL_J1627.0-2425c}

@@

The two year catalog source 2FGL\,J1627.0-2425c was found to be
significantly extended when using photons with energies between 1 \gev
and 100 \gev.  The best fit extension was $0.41\deg\pm0.05\deg$ and the
best fit position is $(l,b)=(353.08\deg, 16.78\deg)$.
The extension significance was $\tsext=31.1$. 
This source is coincident with the one year catalog source 1FGL\,J1628.6-2419c.
A counts map showing this source is
seen in figure \ref{1FGL_J1628.6-2419c}.  To test for source confusion,
we also fit the source instead as two point sources. Since $\tsinc=20.0$
is smaller than \tsext, we conclude that this is an extended source.

@@

\subsection{2FGL\,J1712.4-3941}
\label{section_2FGL_J1712.4-3941}

The two year catalog source 2FGL\,J1712.4-3941 was found to be
spatially extended using photons with energies between 1 \gev and
100 \gev. The source is coincident with the one year catalog source
1FGL\,J1711.7-3944c. We fit an extension of $0.56\deg\pm0\pm04$ with an
extension significance of $\tsext=39.6$. This source was fit to a position
of $(l,b)=(347.25\deg,-0.54\deg)$. Figure \ref{2FGL_J1712.4-3941} shows
a smoothed counts map of this source.

This source is spatially conincident with the SNR RX J1713.7-3946 and was
recently reported by (\cite{rx_j1713_lat}).  To analyze this source,
we used the same background model as the recent LAT publication.
2FGL\,J1715.4-4024c is spatially coincident with Source A and was
moved to the published location of 
$(\text{RA},\text{Dec})=(258.84,-40.46)$. Source
B was added at 
$(\text{RA},\text{Dec})=(258.71,-38.70)$ and Source C was added at
$(\text{RA},\text{Dec})=(257.47,-39.75)$.  Figure \ref{2FGL_J1712.4-3941} shows
the position of these nearby sources on top of a contour of SNR RX
J1713.7-3946 seen in \tev by H.E.S.S (\cite{rx_j1713_hess}).

\subsection{2FGL\,J0851.7-4635}
\label{section_2FGL_J0851.7-4635}

@@

The two year catalog source 2FGL\,J0851.7-4635 was found to be
extended using photons with energies between 10 \gev and 100
\gev. We fit an extension of $1.13\deg\pm0.08\deg$ with an extension
significance of $\tsext=87.2$.  The source was fit to a position of
$(l,b)=(266.29\deg,-1.43\deg)$.  Figure~\ref{Vela_Jr} shows a counts
map of this source.

2FGL\,J0851.7-4635 is spatially coincident with the SNR Vela Jr.  Overlaid
on figure~\ref{Vela_Jr} are contours of Vela Jr. as seen in \tev by
H.E.S.S (\cite{vela_jr_hess}).  The \gev and \tev morphology match well.

\todo[inline]{Add interpretations of Vela Jr.. How to sync with upcoming
publication?}

To get a good fit of the source, we had to remove thee nearby catalog
sources 2FGL\,J0853.5-4711, 2FGL\,J0848.5-4535, and 2FGL\,J0855.4-4625
which are part of the extended source.  In addition, we relocalized
the position of the nearby catalog source 2FGL\,J0854.7-4501 to
$(l,b)=(266.24\deg,0.49\deg)$ to better fit its position at high energies
in the presence of of the extended source.  In addition, we removed the
further away catalog sources 2FGL\,J0858.0-4815 and 2FGL\,J0901.7-4655
because they were not significant above 10 \gev.  After modifying
the region, we found that \tsinc=16.1 which is less than \tsext so we
conclude that the source is extended These modifications are shown in
figure~\ref{Vela_Jr}.

\subsection{2FGL\,J1615.0-5051}
\label{section_2FGL_J1615.0-5051}

@@

The two year catalog source 2FGL\,J1615.0-5051 was found to be
extended using photons with energies between 10 \gev and 100 \gev.
We found an extension of $0.33\deg\pm0.04\deg$ with an extension
significance of \tsext=16.3.  The source was fit to a position of
$(l,b)=(332.38\deg,-0.14\deg)$.  This source is coincident with the one
year catalog source 1FGL\,J1613.6-5100c.  Figure~\ref{1FGL_J1613.6-5100c}
shows a counts map of this source.

This source is less than 1\deg away from 2FGL\,J1615.2-5138 which is
also spatially extended (see section~\ref{section_2FGL_J1615.2-5138}).
To get a good fit of both sources, we had to model both sources as
being spatially extended and iteratively fit the position and extension
of each source until obtaining a global best fit.  Before doing this,
We removed from our model the source 2FGL\,J1614.9-5212 because it is
part of 2FGL\,J1615.2-5138's. Furthermore, we removed
the nearby catalog sources 2FGL\,J1619.7-5040c and 2FGL\,J1620.6-5111c
because they were not significant above 10 \gev.  These modifications
are further described in the caption to figure~\ref{1FGL_J1613.6-5100c}.
After modifying the region, we found that \tsinc=11.9 which is less than
\tsext so we conclude that the source is extended.

This source is spatially coincident with the extended \tev source HESS
J1616-508 (\cite{hess_plane_survey}).  In figure~\ref{1FGL_J1613.6-5100c},
contours of HESS\,J1616-508 are overlaid on 2FGL\,J1615.0-5051.
The H.E.S.S. experiment measured an extension $0.136\pm 0.008$
when fitting the source with an elliptical Gaussian spatial model.
This size corresponds to a 68\% source containment radius of
$\rsixeight=0.21\deg\pm0.01$. This size is comparable to the LAT size
$\rsixeight=0.27\deg\pm0.03$ (see section~\ref{compare_source_size}).
Figure~\ref{hess_seds} shows that the LAT spectrum of 2FGL\,J1615.0-5051
connects smoothly to the H.E.S.S spectrum of HESS\,J1616-508.

\todo[inline]{Add interpretations of HESS\,J1616-508.}

\subsection{2FGL\,J1615.2-5138}
\label{section_2FGL_J1615.2-5138}

The two year catalog source 2FGL\,J1615.2-5138 was found to be
extended using photons with energies between 10 \gev and 100 \gev.
We found an extension of $0.42\deg\pm0.03\deg$ with an extension
significance of \tsext=48.0.  The source was fit to a position
of $(l,b)=(331.66\deg,-0.66\deg)$.  This source is coincident
with the one year catalog source 1FGL\,J1614.7-5138c.  Because 2FGL
J1615.2-5138 is close to 2FGL\,J1615.0-5051, the same model described
in section~\ref{section_2FGL_J1615.0-5051} was used to analyze both
sources. Both sources can be seen in figure~\ref{1FGL_J1613.6-5100c}.
For 2FGL\,J1615.2-5138, \tsinc=37.0 which is less than \tsext so we
conclude that the source is extended.

This source is spatially coincident with the extended \tev source HESS
J1614-518 (\cite{hess_plane_survey}). In figure~\ref{1FGL_J1613.6-5100c},
contours of HESS\,J1614-518 are overlaid on 2FGL\,J1615.2-5138.
The H.E.S.S. experiment measured a Gaussian extension of
$\sigma=0.23\deg\pm0.02\deg$ and $\sigma=0.15\pm0.02$ in the semi-major
and semi-minor axis. This size corresponds to a 68\% containment size
of $\rsixeight=0.35\pm0.03\deg$ and $0.23\pm0.03$.  This elliptical size
matches the LAT size $\rsixeight=0.34\pm0.02$.
Figure~\ref{hess_seds} shows that the LAT spectrum of
2FGL\,J1615.2-5138 connects smoothly to the 
H.E.S.S spectrum of HESS\,J1614-518.

\todo[inline]{Add interpretations of HESS\,J1614-518. Stefan says to
use the Rowell et al, Suzaku observations.}

\subsection{2FGL\,J1632.4-4753c}
\label{section_2FGL_J1632.4-4753c}

@@

The two year catalog source 2FGL\,J1632.4-4753c was found to be
extended using photons with energies between 10 \gev and 100 \gev.
We fit an extension of $0.44\deg\pm0.04\deg$ with an extension
significance of \tsext=64.5.  The source was fit to a position of
$(l,b)=(336.41\deg,0.22\deg)$.  This source is coincident with the one
year catalog source 1FGL\,J1632.9-4802c.  Figure~\ref{1FGL_J1632.9-4802c}
shows a counts map of this source.

To get a good fit of the source, we had to remove from our model
three catalog sources 2FGL\,J1631.7-4720c, 2FGL\,J1630.2-4752,
2FGL J1634.4-4743c.4-4820c that were part of the extended source..
We then iterativly relocalized the source 2FGL\,J1635.4-4717c
to $(l,b)=(337.230\deg,0.346\deg)$ and 2FGL\,J1636.3-4740c to
$(l,b)=(336.968\deg,-0.066\deg)$ while fitting the extension of
2FGL\,J1632.4-4753c.  In addition we removed from our model four
farther away two year catalog sources 2FGL\,J1638.0-4703c, 2FGL
J1628.1-4857c, 2FGL  J1630.1-4615, 2FGL\,J1639.8-4921c because they
were not significant above 10 \gev.  These modifications are shown
in figure~\ref{1FGL_J1632.9-4802c}.  To test for source confusion,
we compared the likelihood fitting this region as one extended source
to the likelihood fitting this region as two point sources. We found
$\tsinc=40.6\loglikelihood\tsext$ which is less than \tsext so we conclude
that this is an extended source.

This extended source is spatially coincident with the extended
\tev source HESS\,J1632-478 (\cite{hess_plane_survey}).  In
figure~\ref{1FGL_J1632.9-4802c}, contours of  HESS\,J1632-478 are
overlaid on 2FGL\,J1635.4-4717c.  H.E.S.S measured an extension of
$\sigma=0.21\pm0.05$ and $0.06\pm0.04$ along the semi-major and semi-minor
axes when fitting the source with an elliptical Gaussian spatial model.
This corresponds to a 68\% containment size $\rsixeight=0.31\pm0.08$
and $0.09\pm0.06$ along the semi-major and semi-minor axis. This
size is consistent with the LAT size $\rsixeight=0.36\pm0.03$.
Figure~\ref{hess_seds} shows that the LAT spectrum of 2FGL\,J1635.4-4717c
connects smoothly to the H.E.S.S spectrum of HESS\,J1632-478.

\todo[inline]{Add interpretation of HESS\,J1632-478.}

\subsection{2FGL\,J1837.3-0700c}
\label{section_2FGL_J1837.3-0700c}

@@

The two year catalog source 2FGL\,J1837.3-0700c was found to be
extended using photons with energies between 10 \gev and 100 \gev.
We fit an extension of $0.35\deg\pm0.08\deg$ with an extension
significance of $\tsext=18.8$.  The source was fit to a position of
$(l,b)=(25.08\deg,0.13\deg)$.  This source is coincident with the one
year catalog source 1FGL\,J1837.5-0659c.  Figure~\ref{1FGL_J1837.5-0659c}
shows a counts map of this source.
